---
title: "Reproducible Document"
author: "rostools"
format: html
editor: visual
---


```{r setup}
#| message: false
#| warning: false


library(tidyverse)

post_meal_data <-
  read_csv2(here::here("data/post-meal-insulin.csv"))

small_post_meal_data <- select(post_meal_data, id, Age, BMI, Group, auc_pg, auc_ins, glykemi)
```

## Colorectal Research Unit

-   Kostyrko Christina
-   Research Assistant

**I live in Copenhagen and have a sister!** *I loooooove research*


## Testing for Git

Such a beautiful sunny day!

## Showing the data

```{r}
post_meal_data

glimpse(post_meal_data)
```

## Plot one continuous variable 

```{r}
#| fig-cap: "Distribution of BMI"
#| label: fig-bmi-histo
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
```
see @fig-bmi-histo

## Exercise: discrete plots

```{r}
#| fig-cap: "Glykemi distribution"
#| label: fig-glykemi-bar
ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```

See @fig-glykemi-bar above for a cool plot!


## Plotting two discrete variables


```{r}
ggplot(post_meal_data, aes(x = Group, fill = as.character(glykemi))) +
  geom_bar(position = position_dodge())
```
## SIde by side plots

```{r fig-bmi-glycemia}
#| fig-cap: "BMI and glycemia, side by side"
#| fig-subcap:
#| - "Distribution of BMI"
#| - "Number of those with glycemia"
#| layout-ncol: 2

ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```


## Plotting two continuous variables

```{r}
#| fig-cap: "Scatter plot of BMI and auc for glucose"

#| lable: "fig-bmi-auc-pg"
ggplot(post_meal_data, aes(x = BMI, y = auc_pg)) +
  geom_point() +
  geom_smooth()
```


## GitHub Token 


## Selecting data

```{r}
select(post_meal_data, Age, BMI, Weight)

select(post_meal_data, -Group)

select(post_meal_data, starts_with("PG"))

select(post_meal_data, ends_with("DXA"))

select(post_meal_data, contains("0"))
```


## Renaming columns

```{r}
small_post_meal_data |>
  rename(
    auc_glucose = auc_pg,
    auc_insuline = auc_ins
  )
```


## Practice - select and rename taksks

```{r}
# Task 1.
post_meal_data |>
  select(contains("OGTT"))

# Task 2.
post_meal_data |>
  select(contains(".."), -contains("..."))

# Task 3.
post_meal_data |>
  rename(
    .minus = ,
     .minus = 
    
    
# Task 4.
post_meal_data |>
  select(id, BMI, Length, Weight, Age |>
           rename(
             Height = Length
           ))
```

```
